Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-07-15 manuscript/appC.Rmd
updates colors in appC figure

@@

```{r plot_it, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE, fig.width=5, fig.cap="Equilibrium cover and 90% quantiles around the mean prediction from the IPM when model error and parameter uncertainty are propogated through the simulation phase for all vital rates except recruitment."}
library(plyr)
library(ggplot2)
setwd("~/Repos/MicroMesoForecast/analysis/")
meanparam_ipm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
##  IPM 
path <- "./ipm/simulations/results/cc_rectest/"
ipmfiles_mean <- list.files(path)
ipmfiles_mean <- ipmfiles_mean[grep("cover", ipmfiles_mean)]
for(file in ipmfiles_mean){
  tmp <- read.csv(paste(path,file,sep=""))
  tmp$model <- "IPM"
  meanparam_ipm <- rbind(meanparam_ipm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_ipm <- meanparam_ipm[2:nrow(meanparam_ipm),]

@@

meanparam_agg <- ddply(ipm_meansims, .(species, climsim, model), summarise,
                       meandiff = mean(propdiff),
                       hidiff = quantile(propdiff, probs = 0.95),
                       lodiff = quantile(propdiff, probs = 0.05))
dgd = position_dodge(width = 0.6)
ggplot(meanparam_agg, aes(color=species))+
  geom_errorbar(aes(x=climsim, ymax=hidiff, ymin=lodiff),
                position=dgd, width=0.25)+
  geom_point(aes(x=climsim, y=meandiff),
                position=dgd, width=0.25)+
  theme_bw()+
#   facet_wrap("species", ncol=1, scales="free")+
  scale_x_discrete(labels=c("+ppt", "+temp", "+ppt&temp"))+
  ylab("Proportional difference")+
  xlab("Climate simulation")
```

>>>>

```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "appC"
opts_chunk$set(fig.path = paste("appC/figure/", basename, "-", sep=""),
               cache.path = paste("appC/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

# PDF-based figures
opts_chunk$set(dev='pdf')
```

@@

```{r plot-options, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

opts_chunk$set(dev='pdf', dev.args=c(version="1.3"))

```

```{r plot_it, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE, fig.width=5, fig.cap="Equilibrium cover and 90% quantiles around the mean prediction from the IPM when model error and parameter uncertainty are propogated through the simulation phase for all vital rates except recruitment.", dependson="plot-options"}
library(plyr)
library(ggplot2)
setwd("~/Repos/MicroMesoForecast/analysis/")
meanparam_ipm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
##  IPM 
path <- "./ipm/simulations/results/cc_rectest/"
ipmfiles_mean <- list.files(path)
ipmfiles_mean <- ipmfiles_mean[grep("cover", ipmfiles_mean)]
for(file in ipmfiles_mean){
  tmp <- read.csv(paste(path,file,sep=""))
  tmp$model <- "IPM"
  meanparam_ipm <- rbind(meanparam_ipm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_ipm <- meanparam_ipm[2:nrow(meanparam_ipm),]

@@

meanparam_agg <- ddply(ipm_meansims, .(species, climsim, model), summarise,
                       meandiff = mean(propdiff),
                       hidiff = quantile(propdiff, probs = 0.95),
                       lodiff = quantile(propdiff, probs = 0.05))
dgd = position_dodge(width = 0.6)
ggplot(meanparam_agg, aes(color=species))+
  geom_errorbar(aes(x=climsim, ymax=hidiff, ymin=lodiff),
                position=dgd, width=0.25)+
  geom_point(aes(x=climsim, y=meandiff),
                position=dgd, width=0.25)+
  theme_bw()+
#   facet_wrap("species", ncol=1, scales="free")+
  scale_x_discrete(labels=c("+ppt", "+temp", "+ppt&temp"))+
  ylab("Proportional difference")+
  xlab("Climate simulation")+
  scale_color_manual(values=cbPalette[1:4])
```
